---
knit: bookdown::preview_chapter
---

# One Compartment Examples

```{r libraries, warning=FALSE, message=FALSE}
# required libraries
library("PKPDmisc")
library("knitr")
library("mrgsolve")
library("ggplot2")
library("dplyr")
```

```{r globalsettings}
opts_chunk$set(fig.height = 6, fig.width = 10, dpi = 300)
```

## One compartment IV

### basic IV 


```{r}
code <- '
$PARAM CL= 1.2, VC=14.3
$CMT GUT CENT
$ADVAN2
$MAIN
pred_CL = CL;
pred_V = VC;
'
model <- mread(code=code, project="compiled_code", model="onecmpt_simple")

```

```{r}
e <- ev(amt=100,rate=50,ii=12, addl=5, cmt=2)
one_cmpt_iv_basic <- model %>% ev(e) %>%
  Req(CENT) %>% mrgsim(end=72,delta=0.1,digits=5)

```

Data can be extracted using the `@data` attribute 

```{r}
one_cmpt_iv_basic@data %>% 
  as.data.frame %>% 
  head %>% 
  kable
```

output from mrgsolve has an inbuilt plot method:

```{r}
plot(one_cmpt_iv_basic) 
```

When filtering, the result is a dataframe, so the `plot` method will
no longer work, and instead it is ideal to turn to ggplot.

```{r}
one_cmpt_iv_basic %>% filter(time < 12) %>% 
  ggplot(aes(x = time, y = CENT)) + geom_line()
```

#### Infusion at Steady State

`ev` understands `ss=1` as an option

```{r}
e <- ev(amt=100,rate=100,ii=12, addl=5, cmt=2,ss=1)
one_cmpt_iv_basic_ss <- model %>% ev(e) %>%
  Req(CENT) %>% mrgsim(end=72,delta=0.1,digits=5)

```

```{r}
one_cmpt_iv_basic_ss@data %>% 
  as.data.frame %>% 
  head %>% 
  kable
```

```{r}
plot(one_cmpt_iv_basic_ss) 
```

```{r}
one_cmpt_iv_basic_ss %>% filter(time < 12) %>% 
  ggplot(aes(x = time, y = CENT)) + geom_line()
```

#### capture individual parameter values

```{r}
one_cmpt_iv <- '
$PARAM TVCL= 1.2, TVVC= 14.3 , WT=70, AGE=50
$CMT GUT CENT
$ADVAN2
$MAIN
double CLi = TVCL*pow(WT/70,0.45)*pow(AGE/50,-0.5);
double Vi = TVVC*(WT/65);
pred_CL = TVCL;
pred_V = TVVC;
$CAPTURE CLi Vi WT AGE
'
model <- mread( model="onecmpt", 
                project="compiled_code",
                code=one_cmpt_iv)
```

```{r}
idata <- expand.idata(WT=seq(40,140),AGE=seq(30,80,10))
out <- model %>% 
  idata_set(idata) %>% 
  mrgsim(end=-1)
```

```{r}
out@data %>% as.data.frame %>% head %>% kable
```

```{r}
out@data %>% as.data.frame %>%
  mutate(AGE = factor(AGE)) %>%
  ggplot(aes(x = WT, y = CLi, color = AGE)) +
 geom_line() + theme_bw() + base_theme()
```


```{r}
devtools::session_info()
```
